---
title: "RegressionModel_Week4_AssignedProject"
author: "Ronda Hutchin"
date: "10/25/2020"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EXECUTIVE SUMMARY

This report is for Motor Trend Magazine, and for the purpose the purpose is to (A) analyzing a data set of a collection of cars,  (B) explore the relationship between a set of variables and miles per gallon (MPG) (outcome) and (C) answer the two questions listed below.

(1) “Is an automatic or manual transmission better for MPG”?
(2) "Quantify the MPG difference between automatic and manual transmissions"?

## Examine the data with STR, HEAD and SUMMARY, and save space hiding results, messages and warnings
```{r results='hide', message=FALSE, warning=FALSE,}
library(ggplot2)
data(mtcars)

library(dplyr)

head(mtcars)
summary(mtcars)
str(mtcars)

```

## EXPLORATORY ANALYSIS
```{r}
with(mtcars, boxplot(mpg~am))

mtcars$am<-as.factor(mtcars$am)
levels(mtcars$am)<-c("Auto", "Manual")


```
You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
