---
title: "RegressionModel_Week4_AssignedProject"
author: "Ronda Hutchin"
date: "10/25/2020"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EXECUTIVE SUMMARY: This report is for Motor Trend Magazine, and for the purpose the purpose is to (A) analyzing a data set of a collection of cars,  (B) explore the relationship between a set of variables and miles per gallon (MPG) (outcome) and (C) answer the two questions listed below.

(1) “Is an automatic or manual transmission better for MPG”?
(2) "Quantify the MPG difference between automatic and manual transmissions"?
## Examine the data with STR, HEAD and SUMMARY, and save space hiding results, messages and warnings
```{r results='hide', message=FALSE, warning=FALSE,}
library(ggplot2)
data(mtcars)
library(dplyr)
head(mtcars)
summary(mtcars)
str(mtcars)
```
## EXPLORATORY ANALYSIS using boxplot (in appendix A), getting the mean of each type and doing a t-test. The below results has a p-value = 0.001374 which iswithin the 95% confidence interval.  It appears the difference between the mean MPG of Automatic and Manual cars is significant, but further analysis is needed.
```{r}
aggregate(mpg ~ am, data = mtcars, mean)

Automatic <- mtcars[mtcars$am == "0",]
Manual <- mtcars[mtcars$am == "1",]

t.test(Automatic$mpg, Manual$mpg)
```
## FURTHER ANALYSIS using a Regression model good for "binary" models since we have two transmission types represented by 0 and 1.  The results are promising as shown below - note the probability and AIC values.  More analysis is needed
```{r}
fit1<-glm(mtcars$am~mtcars$mpg, family ="binomial")
exp(fit1$coefficients)
summary(fit1)
```

## FURTHER ANALYSIS using Regression model to consider other vairables which is why I chose a multivariable regression model to also consider cyclinders and horsepower.  Results are below for fit2 to the last fit7
```{r}
fit2<-lm(mpg~factor(am)+factor(cyl)+hp, data=mtcars)
anova(fit2)
summary(fit2)
fit3<-lm(mpg ~ factor(am) + factor(cyl), data=mtcars)
fit4<-lm(mpg ~ factor(am) + factor(cyl)+ hp, data=mtcars)
fit5<-lm(mpg ~ factor(am) + factor(cyl)+ wt +hp, data=mtcars)
fit6<-lm(mpg ~ factor(am) + factor(cyl)+ wt +hp +disp, data=mtcars)
fit7<-lm(mpg ~ factor(am) + factor(cyl)+ wt +hp +disp+qsec+factor(gear)+factor(carb), data=mtcars)
anova(fit3,fit4,fit5,fit6,fit7)
```
## CONCLUSION for  Question (1) & (2): Transmission type is significant in it’s relationship with MPG - it has lower value significance when considered with weight AND qsec (acceleration) - cars with manual transmission add 14.079 + (-4.141)*wt more MPG (miles per gallon) on average than cars with automatic transmission. The multivairable regression test results suggest that fuel efficiency is approx. 2.94 MPG higher for Manual cars over Automatic.   
## APPENDIX 
Results of boxplot and multivariable analysis
```{r}
with(mtcars, boxplot(mpg~am, xlab="Transmission (0 = Automatic, 1 = Manual)", ylab="MPG"))
par(mfrow = c(2, 2))
plot(fit2)
```

